Figures

### 2020-03-04 figures/08_exploratory_dotplot.Rmd
rm tn and tp from heatmap, closes #16
cleanup correlation heatmap

dt       <- readRDS("../data/dt_scaled.rds")
dt_sub   <-  dt %>% 
  dplyr::select(-lagoslakeid) %>%
  # dplyr::select(tp, tn, lake_area_ha:wheat, 
  #               matches("cultivated_crops")) %>%
  # dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  # dplyr::select(-mixed.crop, -matches("other"), -forage, 
  #               -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  # dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  janitor::remove_empty("cols") %>%
  data.frame(stringsAsFactors = FALSE)

@@

dt_tp_rows       <- dt_tp_hmap$rowname
dt_tp_hmap            <- dt_tp_hmap %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tp_hmap) <- dt_tp_rows

# prettyfi variable labels
pretty_names <- pred_key$pretty[match(names(dt_tp_hmap), pred_key$var)] 
pretty_names <- pretty_names[!is.na(pretty_names)]
names(dt_tp_hmap)[which(!is.na(match(names(dt_tp_hmap), pred_key$var)))] <- 
  pretty_names
pretty_names <- pred_key$pretty[match(row.names(dt_tp_hmap), pred_key$var)] 
pretty_names <- pretty_names[!is.na(pretty_names)]
row.names(dt_tp_hmap)[which(!is.na(match(row.names(dt_tp_hmap), pred_key$var)))] <- 
  pretty_names

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
```

>>>>

dt       <- readRDS("../data/dt_scaled.rds")
dt_sub   <-  dt %>% 
  dplyr::select(names(.)[names(.) %in% c(pred_key$var, "tn", "tp")]) %>%
  # dplyr::select(-lagoslakeid) %>%
  # dplyr::select(tp, tn, lake_area_ha:wheat, 
  #               matches("cultivated_crops")) %>%
  # dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  # dplyr::select(-mixed.crop, -matches("other"), -forage, 
  #               -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  # dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  janitor::remove_empty("cols") %>%
  data.frame(stringsAsFactors = FALSE)

@@

dt_tp_rows       <- dt_tp_hmap$rowname
dt_tp_hmap            <- dt_tp_hmap %>%
  dplyr::select(-rowname) # %>%
  # mutate_all(abs)
row.names(dt_tp_hmap) <- dt_tp_rows

# prettyfi variable labels
pretty_names <- pred_key$pretty[match(names(dt_tp_hmap), pred_key$var)] 
pretty_names <- pretty_names[!is.na(pretty_names)]
names(dt_tp_hmap)[which(!is.na(match(names(dt_tp_hmap), pred_key$var)))] <- 
  pretty_names
pretty_names <- pred_key$pretty[match(row.names(dt_tp_hmap), pred_key$var)] 
pretty_names <- pretty_names[!is.na(pretty_names)]
row.names(dt_tp_hmap)[
  which(!is.na(match(row.names(dt_tp_hmap), pred_key$var)))] <- pretty_names

# rm tp and tn also row crop ag and stream-buffer ag
dt_tp_hmap <- dplyr::select(dt_tp_hmap, -tp, -tn, 
                            -`Row-crop Ag`, -`Stream-buffer Ag`)
dt_tp_hmap <- dt_tp_hmap[!(row.names(dt_tp_hmap) %in% 
                              c("tp", "tn", "Row-crop Ag", "Stream-buffer Ag")),]

# manually sort according to the clustering shown when cluster_rows/cols TRUE
# see jsta/jsta #15 
rowcol_order <- c("Manure N", "Manure P", "Fertilizer N", 
                  "Fertilizer P", "N input", "P input", 
                  "Max depth", "Watershed-lake ratio",
                  "N deposition", "Baseflow", "Clay",
                  "Wetlands", "Pasture", "Precipitation",
                  "Soil organic carbon", "Wetland potential",
                  "Buffer natural", "Buffer Ag", "Ag", 
                  "Soybeans", "Forest", "Corn")
dt_tp_hmap <- dt_tp_hmap[match(rowcol_order, row.names(dt_tp_hmap)),]
dt_tp_hmap <- dt_tp_hmap[,match(rowcol_order, names(dt_tp_hmap))]

dt_tp_hmap_abs <- mutate_all(dt_tp_hmap, abs) %>%
  data.frame()
row.names(dt_tp_hmap_abs) <- rowcol_order
pheatmap::pheatmap(
  t(dt_tp_hmap_abs),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)

pheatmap::pheatmap(
  t(dt_tp_hmap),
  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
  #                                          "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
```
